\Huge\textbf{QuantoniumOS Developer Manual}\\[0.5em] \Large Complete Full-Stack Architecture, Proofs, and Operations\\[0.3em] \normalsize Technical Reference

### 2025-12-02 papers/dev_manual_tech_temp.tex
Update benchmarks and documentation
- Fixed H3 Hybrid Cascade detection in Class B benchmarks
- Added missing os import and corrected path resolution
- Integrated patent compliance report (USPTO 19/169,399)
- Updated dev manual to Version 3.0 (128 pages)
- Added comprehensive variants taxonomy and hybrid codecs
- Generated benchmark report PDF with honest framing
- Archived deprecated manual versions
- Fixed pyfftw version detection compatibility

\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tocloft}
\geometry{margin=1in}
\newcommand{\phig}{\ensuremath{\Phi}}% golden ratio symbol used inline
 #1\textbf{]}}
 #1\textbf{]}}

@@

@@

QuantoniumOS is a \textbf{wave-space operating system} that provides:
\begin{enumerate}
\item \textbf{Transform Layer}: Unified API for 13 unitary transform variants via the Phi-Resonance Fourier Transform ($\Phi$-RFT)
\item \textbf{Middleware Engine}: Binary $\leftrightarrow$ Wave conversion (RFTMW.py) enabling wave-space computation
\item \textbf{Application Framework}: Desktop (PyQt5) and mobile (React Native) applications using RFT primitives
\item \textbf{Hardware Abstraction}: SystemVerilog RTL for FPGA deployment of RFT kernels
\item \textbf{Quantum Simulator}: Classical simulation of quantum circuits using RFT as gate operations
\end{enumerate}

@@

\textbf{Market}: Quantum software companies (Zapata, Xanadu, Rigetti) spend \$50K--\$200K/month on IBM/AWS quantum cloud time. QuantoniumOS enables:
\begin{itemize}
\item Local development at O(n) memory cost
\item 10M qubit simulations on commodity hardware
\item Fast iteration without cloud billing
\end{itemize}
\textbf{Limitation}: Not exact simulation---symbolic compression for algorithm prototyping only.

@@

\textbf{Market}: Sound designers for film/games (\$50B industry). Current limitation: All synthesis uses integer or rational frequency ratios. QuantoniumOS enables:
\begin{itemize}
\item $\phi$-spaced additive synthesis (patent-pending)
\item Inharmonic but aesthetically structured timbres
\item Audio fingerprinting via irrational spectral signatures
\end{itemize}
\textbf{Limitation}: 7× latency overhead means offline rendering only (not real-time performance).

@@

\textbf{Market}: Cryptography researchers preparing for NIST PQC transitions. QuantoniumOS enables:
\begin{itemize}
\item Rapid prototyping of SIS-based hash functions
\item 48-round Feistel cipher with $\phi$-parameterized keys
\item Avalanche testing (50\% achieved)
\end{itemize}
\textbf{Critical Limitation}: NO security proofs. This is a research tool, NOT production crypto. Use NIST-approved algorithms (Kyber, Dilithium) for real systems.

@@

QuantoniumOS implements the Phi-Resonance Fourier Transform ($\Phi$-RFT), a novel unitary transform defined as $\Psi = D_\phi C_\sigma F$ where $F$ is the DFT, $C_\sigma$ is a quadratic chirp phase, and $D_\phi$ is a golden-ratio modulated diagonal matrix. The transform is provably distinct from Linear Canonical Transforms (LCT) and achieves $\mathcal{O}(n \log n)$ complexity via FFT.

\section{Patent-Protected Architecture}

\subsection{USPTO Application 19/169,399}

\textbf{Title}: Hybrid Computational Framework for Quantum and Resonance Simulation\\
\textbf{Filing Date}: April 3, 2025\\
\textbf{Inventor}: Luis Michael Minier\\
\textbf{Status}: Pre-examination formalities completed (August 11, 2025)

QuantoniumOS implements four patented claims that form the foundation of the system:

\subsubsection{Claim 1: Symbolic Resonance Fourier Transform Engine}

The core transform engine comprising:

\begin{itemize}
\item \textbf{Symbolic representation module}: Expresses quantum state amplitudes as algebraic forms enabling O(n) memory scaling instead of O($2^n$) for traditional quantum simulation
\item \textbf{Phase-space coherence retention}: Maintains structural dependencies between symbolic amplitudes and phase interactions using golden ratio ($\phi = 1.618...$) parameterization
\item \textbf{Topological embedding layer}: Maps symbolic amplitudes into structured manifolds preserving winding numbers, node linkage, and transformation invariants
\item \textbf{Symbolic gate propagation}: Supports quantum logic operations (Hadamard, Pauli-X) without collapsing symbolic entanglement structures
\end{itemize}

\textbf{Implementation}: \texttt{algorithms/rft/kernels/kernel/quantum\_symbolic\_compression.c}, \texttt{algorithms/rft/quantum/quantum\_gates.py}

\textbf{Performance}: 10M qubits simulated @ 19.1 Mq/s, unitarity error $< 10^{-12}$

\subsubsection{Claim 2: Resonance-Based Cryptographic Subsystem}

Experimental cryptographic primitives (RESEARCH ONLY - NO SECURITY PROOFS):

\begin{itemize}
\item \textbf{Symbolic waveform generation}: Constructs amplitude-phase modulated signatures from input data
\item \textbf{Topological hashing module}: Extracts waveform features into Bloom-like filters representing cryptographic identities
\item \textbf{Dynamic entropy mapping}: Continuous modulation of key material based on symbolic resonance states
\item \textbf{Recursive modulation controller}: Modifies waveform structure in real time for diffusion
\end{itemize}

\textbf{Implementation}: \texttt{algorithms/rft/quantum/geometric\_waveform\_hash.py}, \texttt{algorithms/rft/crypto/enhanced\_cipher.py}

\textbf{Performance}: 50\% avalanche effect, 48-round Feistel structure

\textbf{WARNING}: This is a research tool for post-quantum cryptography experimentation. Do NOT use in production systems. Use NIST-approved algorithms (AES-256, Kyber, Dilithium) for real security needs.

\subsubsection{Claim 3: Geometric Structures for RFT-Based Cryptographic Waveform Hashing}

Novel geometric coordinate system for hash generation:

\begin{itemize}
\item \textbf{Polar-to-Cartesian transformations}: Golden ratio scaling applied to harmonic relationships: $x[k] = r[k] \times \cos(\theta[k]) \times \phi^{k/N}$
\item \textbf{Complex geometric coordinate generation}: Exponential transforms creating quaternion-like representations
\item \textbf{Topological winding number computation}: Discrete contour integration for cryptographic signatures
\item \textbf{Euler characteristic approximation}: Genus estimation from winding number distribution
\item \textbf{Manifold-based hash generation}: Preserves geometric relationships in cryptographic output space (>95\% correlation)
\end{itemize}

\textbf{Implementation}: \texttt{algorithms/rft/quantum/geometric\_waveform\_hash.py}, \texttt{algorithms/rft/quantum/enhanced\_topological\_qubit.py}

\textbf{Note}: Corrected from original filing to reflect actual implementation using geometric coordinate systems instead of tetrahedral simplices

\subsubsection{Claim 4: Hybrid Mode Integration}

Unified computational framework integrating all subsystems:

\begin{itemize}
\item \textbf{Coherent propagation}: Symbolic amplitude and phase-state transformations propagate coherently across encryption and storage layers
\item \textbf{Dynamic resource allocation}: Maintains <80\% CPU, <70\% memory utilization under optimal scheduling
\item \textbf{Synchronized orchestration}: Unified orchestrator routes tasks across 3 assembly engines (optimized, unitary, vertex)
\item \textbf{Topological integrity maintenance}: Surface code error correction and stabilizer checks
\item \textbf{Modular phase-aware architecture}: Suitable for symbolic simulation, secure communication, nonbinary data management
\end{itemize}

\textbf{Implementation}: \texttt{algorithms/rft/kernels/unified/kernel/unified\_orchestrator.c}, \texttt{algorithms/rft/kernels/quantonium\_os.py}

\textbf{Performance}: >90\% phase correlation across subsystems, 1-10 MB/s throughput

\subsection{Files Practicing Patent Claims}

The following files implement claim-bearing inventions and are licensed under LICENSE-CLAIMS-NC.md (research/education only). All other files use AGPL-3.0-or-later. See \texttt{CLAIMS\_PRACTICING\_FILES.txt} for complete list.

\textbf{Core claim-practicing files}:
\begin{itemize}
\item \textbf{Claim 1}: quantum\_symbolic\_compression.*, symbolic\_unitary.py, quantum\_gates.py, enhanced\_topological\_qubit.py
\item \textbf{Claim 2}: geometric\_waveform\_hash.py, enhanced\_cipher.py, feistel\_round48.*
\item \textbf{Claim 3}: geometric\_hashing.py, enhanced\_topological\_qubit.py (coordinate systems)
\item \textbf{Claim 4}: unified\_orchestrator.*, quantonium\_os.py, rft\_kernel.h
\end{itemize}

@@

The system implements:
\begin{enumerate}
  \item \textbf{13 unitary transform variants} (unitary by construction) with distinct spectral properties
  \item \textbf{Hybrid compression pipelines} achieving 1.95-2.83× compression on specific workloads
  \item \textbf{Experimental 48-round Feistel cipher} with ~50\% avalanche (no formal proofs - research only)
  \item \textbf{Synthesizable SystemVerilog RTL} for FPGA deployment
  \item \textbf{React Native mobile app} and PyQt5 desktop applications
  \item \textbf{Unified orchestrator} routing tasks across multiple optimized assembly engines
\end{enumerate}

@@

\subsection{Directory Overview}

@@

\paragraph{Workflows (\texttt{.github/workflows/}):}
\begin{itemize}
  \item \texttt{spdx-headers.yml} --- Automatically adds license headers to all files
\end{itemize}

@@

The SPDX workflow distinguishes between AGPL-3.0 files and Claims-NC files using the list in \texttt{CLAIMS\_PRACTICING\_FILES.txt}. The agent spec defines TODO items for:
\begin{enumerate}
  \item WaveField abstraction layer
  \item Binary-to-WaveField middleware
  \item Audio/Visual/Physics/Crypto labs
  \item Comprehensive test coverage
\end{enumerate}

@@

\subsection[Closed-Form Phi-RFT]{Closed-Form \phig-RFT}

@@

@@

Since $F$, $C_\sigma$, and $D_\phi$ are all unitary (diagonal with unit-modulus entries):
\[
\Psi^\dagger \Psi = F^\dagger C_\sigma^\dagger D_\phi^\dagger D_\phi C_\sigma F = F^\dagger C_\sigma^\dagger C_\sigma F = F^\dagger F = I
\]
Each diagonal matrix satisfies $D^\dagger D = I$ because $|e^{i\theta}| = 1$ for all $\theta$.

@@

\subsubsection{Technical Implementation}

@@

The golden-ratio phase $\{k/\phi\}$ is \emph{not quadratic}. The second difference $\Delta^2\{k/\phi\}$ takes values in $\{-1, 0, 1\}$ and is not constant. Therefore, $D_\phi$ cannot be represented as $Ak^2 + Bk + C$, proving non-membership in the Linear Canonical Transform (LCT) family.

@@

\begin{lstlisting}[language=Python, caption={RFT Status Module}]
import functools

@functools.lru_cache(maxsize=1)
def get_rft_status():
    """
    Returns cached status dictionary about RFT kernel.

    Returns:
        dict with keys:
        - 'native_available': bool
        - 'implementation': 'native' or 'python'
        - 'version': string
    """
    try:
        import rft_native_kernel
        return {
            'native_available': True,
            'implementation': 'native',
            'version': rft_native_kernel.__version__
        }
    except ImportError:
        return {
            'native_available': False,
            'implementation': 'python',
            'version': 'numpy-fft'
        }

@@

@@

\begin{lstlisting}[language=Python, caption={Quantum Gate Classes}]
class QuantumGate:
    """Base class for quantum gate matrices."""

    def __init__(self, matrix, name):
        self.matrix = np.array(matrix, dtype=np.complex128)
        self.name = name
        self._validate_unitary()

    def _validate_unitary(self):
        I = np.eye(self.matrix.shape[0])
        error = np.linalg.norm(self.matrix.conj().T @ self.matrix - I)
        if error > 1e-10:
            raise ValueError(f"{self.name} is not unitary (error={error})")

    def apply(self, state):
        return self.matrix @ state

class PauliX(QuantumGate):
    """Bit-flip gate (quantum NOT)."""
    def __init__(self):
        super().__init__([[0, 1], [1, 0]], 'X')

class PauliY(QuantumGate):
    """Bit+phase flip gate."""
    def __init__(self):
        super().__init__([[0, -1j], [1j, 0]], 'Y')

class PauliZ(QuantumGate):
    """Phase-flip gate."""
    def __init__(self):
        super().__init__([[1, 0], [0, -1]], 'Z')

class Hadamard(QuantumGate):
    """Creates superposition."""
    def __init__(self):
        h = 1/np.sqrt(2)
        super().__init__([[h, h], [h, -h]], 'H')

class RFTGate(QuantumGate):
    """RFT as a quantum gate."""
    def __init__(self, n):
        from algorithms.rft.core.closed_form_rft import rft_matrix
        super().__init__(rft_matrix(n), f'RFT-{n}')
\end{lstlisting}

@@

\begin{lstlisting}[language=Python, caption={Topological Qubit Types}]
from enum import Enum

class TopoQubitType(Enum):
    """Types of topological qubits."""
    ABELIAN_ANYON = "abelian"      # Simple anyons
    NON_ABELIAN_ANYON = "non_abelian"  # Complex anyons (universal)
    MAJORANA_FERMION = "majorana"  # Half-electron quasiparticle

class TopologicalInvariants:
    """
    Topological invariants for characterizing quantum states.
    These numbers don't change under smooth deformations.
    """
    def __init__(self):
        self.winding_number = 0   # Counts loops
        self.chern_number = 0     # Magnetic flux quanta
        self.berry_phase = 0.0    # Geometric phase

class TopoQubit:
    """
    Simulated topological qubit with error correction.
    """
    def __init__(self, qubit_type=TopoQubitType.ABELIAN_ANYON):
        self.qubit_type = qubit_type
        self.state = np.array([1, 0], dtype=np.complex128)
        self.invariants = TopologicalInvariants()

    def braid(self, other_qubit):
        """
        Braid two anyons around each other.
        This is the fundamental operation in topological QC.
        """
        if self.qubit_type == TopoQubitType.NON_ABELIAN_ANYON:
            # Non-trivial braiding matrix
            theta = np.pi / 4
            R = np.array([
                [np.exp(-1j*theta), 0],
                [0, np.exp(1j*theta)]
            ])
            self.state = R @ self.state
\end{lstlisting}

@@

@@

\begin{lstlisting}[language=Python, caption={Vertex Codec for Model Compression}]
class VertexContainer:
    """
    Container for RFT vertex data.
    Stores amplitude and phase separately for efficient compression.
    """
    def __init__(self, amplitudes, phases, shape, dtype):
        self.amplitudes = amplitudes  # Magnitudes |c_k|
        self.phases = phases          # Angles arg(c_k)
        self.shape = shape            # Original tensor shape
        self.dtype = dtype            # Original data type

class RFTVertexCodec:
    """
    Encode tensors as RFT vertex representations.
    Lossless for floating-point data.
    """

    def encode_tensor(self, tensor):
        """
        Encode tensor to vertex container.

        Process:
        1. Flatten tensor
        2. Apply RFT
        3. Extract amplitude and phase
        """
        flat = tensor.flatten().astype(np.complex128)
        coeffs = rft_forward(flat)

        amplitudes = np.abs(coeffs)
        phases = np.angle(coeffs)

        return VertexContainer(
            amplitudes=amplitudes,
            phases=phases,
            shape=tensor.shape,
            dtype=tensor.dtype
        )

    def decode_tensor(self, container):
        """
        Reconstruct tensor from vertex container.
        """
        # Reconstruct complex coefficients
        coeffs = container.amplitudes * np.exp(1j * container.phases)

        # Inverse RFT
        flat = rft_inverse(coeffs).real

        # Reshape and cast
        return flat.reshape(container.shape).astype(container.dtype)

    def encode_state_dict(self, state_dict):
        """Encode PyTorch model state dict."""
        encoded = {}
        for name, tensor in state_dict.items():
            encoded[name] = self.encode_tensor(tensor.numpy())
        return encoded

@@

\subsubsection{The Algorithm}

@@

\begin{lstlisting}[language=Python, caption={Geometric Hash Functions}]
class RFTGeometricHash:
    """
    RFT-enhanced quantum-safe geometric hashing.
    """

    def __init__(self, dim=3, hash_bits=256):
        self.dim = dim
        self.hash_bits = hash_bits
        self.rft = UnitaryRFT(hash_bits // 8)

    def hash_point(self, point):
        """
        Hash a single point to fixed-size digest.
        """
        # Normalize coordinates
        coords = np.array(point, dtype=np.float64)
        coords = coords / (np.linalg.norm(coords) + 1e-10)

        # Pad to RFT dimension
        padded = np.zeros(self.hash_bits // 8)
        padded[:len(coords)] = coords

        # Apply RFT
        hashed = self.rft.forward(padded)

        # Convert to bytes
        return np.abs(hashed).astype(np.uint8).tobytes()

    def hash_point_cloud(self, points):
        """Hash collection of points."""
        combined = np.zeros(self.hash_bits // 8)
        for point in points:
            point_hash = np.frombuffer(
                self.hash_point(point), 
                dtype=np.uint8
            ).astype(float)
            combined = np.abs(self.rft.forward(combined + point_hash))
        return combined.astype(np.uint8).tobytes()
\end{lstlisting}

@@

The middleware layer in \texttt{quantonium\_os\_src/engine/RFTMW.py} provides the bridge between binary data and wave-space computation.

\subsection{Data Flow: Binary $\to$ Wave $\to$ Compute $\to$ Binary}

@@

%==============================================================================
\part{Desktop Applications}
%==============================================================================

@@

\subsubsection{Architecture}

@@

\paragraph{File:} \texttt{src/apps/q\_notes.py}

@@

\paragraph{File:} \texttt{src/apps/q\_vault.py}

@@

\paragraph{File:} \texttt{src/apps/qshll\_system\_monitor.py}

@@

The SystemVerilog implementation in \texttt{hardware/} provides synthesizable RTL for FPGA deployment.

%==============================================================================
\part{Hardware Implementation}
%==============================================================================

@@

\begin{lstlisting}[language=Verilog, caption={CORDIC Sine/Cosine Calculator}]
module cordic_sincos #(
    parameter WIDTH = 32,
    parameter ITERATIONS = 16
)(
    input  wire clk,
    input  wire rst_n,
    input  wire start,
    input  wire [WIDTH-1:0] angle,      // Input angle in radians (Q16.16)
    output reg  [WIDTH-1:0] cos_out,    // cos(angle)
    output reg  [WIDTH-1:0] sin_out,    // sin(angle)
    output reg  valid
);

    // Precomputed arctan table in Q16.16
    // atan(2^-i) for i = 0..15
    localparam [WIDTH-1:0] ATAN_TABLE [0:15] = '{
        32'h0000_C910,  // atan(1)     = 45.000 deg = 0.785 rad
        32'h0000_76B2,  // atan(0.5)   = 26.565 deg = 0.464 rad
        32'h0000_3EB7,  // atan(0.25)  = 14.036 deg = 0.245 rad
        32'h0000_1FD5,  // atan(0.125) = 7.125 deg  = 0.124 rad
        32'h0000_0FFB,  // ...
        32'h0000_07FF,
        32'h0000_0400,
        32'h0000_0200,
        32'h0000_0100,
        32'h0000_0080,
        32'h0000_0040,
        32'h0000_0020,
        32'h0000_0010,
        32'h0000_0008,
        32'h0000_0004,
        32'h0000_0002
    };

    // CORDIC gain compensation: K = prod(cos(atan(2^-i)))
    // K^-1 approx 1.6468 in Q16.16 = 0x1A827
    localparam [WIDTH-1:0] K_INV = 32'h0001_A827;

    // Working registers
    reg signed [WIDTH-1:0] x, y, z;
    reg [4:0] iteration;
    reg running;

    always_ff @(posedge clk or negedge rst_n) begin
        if (!rst_n) begin
            x <= 0;
            y <= 0;
            z <= 0;
            iteration <= 0;
            running <= 0;
            valid <= 0;
        end else if (start && !running) begin
            // Initialize: start with unit vector on x-axis
            x <= K_INV;  // Start with gain compensation
            y <= 0;
            z <= angle;
            iteration <= 0;
            running <= 1;
            valid <= 0;
        end else if (running) begin
            if (iteration < ITERATIONS) begin
                // CORDIC iteration
                if (z >= 0) begin
                    // Rotate counterclockwise
                    x <= x - (y >>> iteration);
                    y <= y + (x >>> iteration);
                    z <= z - ATAN_TABLE[iteration];
                end else begin
                    // Rotate clockwise
                    x <= x + (y >>> iteration);
                    y <= y - (x >>> iteration);
                    z <= z + ATAN_TABLE[iteration];
                end
                iteration <= iteration + 1;
            end else begin
                // Done
                cos_out <= x;
                sin_out <= y;
                valid <= 1;
                running <= 0;
            end
        end else begin
            valid <= 0;
        end
    end

@@

%==============================================================================
\part{Testing, Scripts, and Tools}
%==============================================================================

@@

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{File/Directory} & \textbf{Purpose} \\
\midrule
\texttt{App.tsx} & Main entry point with splash screen \\
\texttt{app.json} & Expo configuration \\
\texttt{package.json} & Node.js dependencies \\
\texttt{src/algorithms/} & Mobile RFT implementations \\
\texttt{src/components/} & Reusable UI components \\
\texttt{src/screens/} & App screens (home, settings, etc.) \\
\texttt{src/navigation/} & React Navigation setup \\
\texttt{src/utils/} & Utility functions \\
\texttt{src/constants/} & App constants and themes \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{@{}p{5.5cm}p{7.5cm}@{}}
\toprule
\textbf{Script} & \textbf{Purpose} \\
\midrule
\multicolumn{2}{l}{\textit{Validation Scripts}} \\
\texttt{irrevocable\_truths.py} & Validates 7 variants and fundamental theorems \\
\texttt{verify\_scaling\_laws.py} & Verifies compression scaling laws \\
\texttt{verify\_rate\_distortion.py} & Rate-distortion analysis \\
\texttt{verify\_braided\_comprehensive.py} & Braided structure validation \\
\texttt{validate\_paper\_claims.py} & Validates claims from research paper \\
\midrule
\multicolumn{2}{l}{\textit{Generation Scripts}} \\
\texttt{generate\_all\_theorem\_figures.py} & Generate figures for all theorems \\
\texttt{generate\_rft\_gifs.py} & Create animated RFT visualizations \\
\texttt{generate\_pdf\_figures\_for\_latex.py} & PDF figures for LaTeX papers \\
\texttt{generate\_rft\_gifs\_simple.py} & Simplified GIF generation \\
\midrule
\multicolumn{2}{l}{\textit{Utility Scripts}} \\
\texttt{quantonium\_boot.py} & Desktop boot/launcher \\
\texttt{build.py} & Build system script \\
\texttt{md\_to\_pdf.py} & Markdown to PDF converter \\
\texttt{analyze\_quantum\_chaos.py} & Quantum chaos metrics \\
\texttt{compile\_paper.sh} & Compile LaTeX papers \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{@{}p{5cm}p{8cm}@{}}
\toprule
\textbf{Tool} & \textbf{Purpose} \\
\midrule
\multicolumn{2}{l}{\textit{Benchmarking}} \\
\texttt{uspto\_benchmark\_suite.py} & Generate USPTO patent evidence \\
\texttt{benchmark\_runner.py} & Run performance benchmarks \\
\midrule
\multicolumn{2}{l}{\textit{Compression}} \\
\texttt{compression\_pipeline.py} & Full compression pipeline \\
\texttt{rft\_hybrid\_compress.py} & Hybrid RFT compression \\
\texttt{rft\_encode\_model.py} & Encode model weights \\
\texttt{rft\_decode\_model.py} & Decode model weights \\
\texttt{real\_hf\_model\_compressor.py} & HuggingFace model compression \\
\midrule
\multicolumn{2}{l}{\textit{Development}} \\
\texttt{spdx\_inject.py} & Add SPDX license headers \\
\texttt{generate\_repo\_inventory.py} & Generate repository inventory \\
\texttt{restructure\_dry\_run.py} & Preview restructuring changes \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Directory} & \textbf{Investigation} \\
\midrule
\texttt{ascii\_wall/} & Testing compression on pure ASCII text \\
\texttt{corpus/} & Benchmark corpus (text, audio, image samples) \\
\texttt{entropy/} & Entropy analysis of RFT coefficients \\
\texttt{fibonacci/} & Fibonacci sequence compression \\
\texttt{hypothesis\_testing/} & Statistical validation of claims \\
\texttt{sota\_benchmarks/} & State-of-the-art comparisons \\
\texttt{tetrahedral/} & Tetrahedral lattice experiments \\
\bottomrule
\end{tabular}
\end{center}

@@

\paragraph{Virtual Environment:}
\begin{verbatim}
# Create isolated Python environment
python3 -m venv .venv

@@

\paragraph{Standard Development Container:}
\begin{verbatim}
# Build the image
docker build -t quantoniumos .

@@

%------------------------------------------------------------------------------
\subsection{System Architecture}
%------------------------------------------------------------------------------

@@

The RFT matrix $\Psi_{jk} = n^{-1/2} e^{i\theta_{jk}}$ where $\theta_{jk} = -2\pi jk/n + \pi\sigma k^2/n + 2\pi\beta\{k/\phi\}$. The structured phase patterns enable efficient compression of golden-ratio signals.

@@

The phase function $\varphi(k) = 2\pi\beta\{k/\phi\}$ where $\{x\} = x - \lfloor x \rfloor$ is the fractional part. This creates a quasi-periodic modulation with period $\phi \approx 1.618$. The non-quadratic nature proves non-membership in the LCT class.

@@

For a signal $x[n] = \sum_m a_m e^{2\pi i \phi^m n / N}$, the RFT coefficients exhibit sparsity $S > 61.8\%$ (Theorem 3). The figure shows empirical sparsity reaching 98.63\% at $N=512$ for ideal golden-ratio signals.

@@

The Frobenius norm $\|U^\dagger U - I\|_F$ measures deviation from perfect unitarity. Values $< 10^{-14}$ are consistent with IEEE 754 double-precision floating-point roundoff, confirming the implementation matches the mathematical specification.

@@

The frequency spectra validates correct phase accumulation in the CORDIC pipeline. Peak locations match theoretical predictions to within 1 frequency bin.

>>>>

\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tocloft}
\geometry{margin=1in}
\newcommand{\phig}{\ensuremath{\Phi}}% golden ratio symbol used inline

@@

\begin{itemize}
\end{itemize}

@@

\item \textbf{Transform Layer}: Unified API for 13 unitary transform variants via the Phi-Resonance Fourier Transform ($\Phi$-RFT)
\item \textbf{Middleware Engine}: Binary $\leftrightarrow$ Wave conversion (RFTMW.py) enabling wave-space computation
\item \textbf{Application Framework}: Desktop (PyQt5) and mobile (React Native) applications using RFT primitives
\item \textbf{Hardware Abstraction}: SystemVerilog RTL for FPGA deployment of RFT kernels
\item \textbf{Quantum Simulator}: Classical simulation of quantum circuits using RFT as gate operations
\end{enumerate}}

@@

\item Local development at O(n) memory cost
\item 10M qubit simulations on commodity hardware
\item Fast iteration without cloud billing
\end{itemize}
\textbf{Limitation}: Not exact simulation---symbolic compression for algorithm prototyping only.
}

@@

\item $\phi$-spaced additive synthesis (patent-pending)
\item Inharmonic but aesthetically structured timbres
\item Audio fingerprinting via irrational spectral signatures
\end{itemize}
\textbf{Limitation}: 7× latency overhead means offline rendering only (not real-time performance).
}

@@

\item Rapid prototyping of SIS-based hash functions
\item 48-round Feistel cipher with $\phi$-parameterized keys
\item Avalanche testing (50\% achieved)
\end{itemize}
\textbf{Critical Limitation}: NO security proofs. This is a research tool, NOT production crypto. Use NIST-approved algorithms (Kyber, Dilithium) for real systems.
}

@@

@@

  \item \textbf{Compression:} Making files smaller without losing information
  \item \textbf{Security:} Scrambling data so only authorized people can read it
  \item \textbf{Audio/Video:} Processing sounds and images in unique ways
  \item \textbf{Science:} Simulating quantum physics on regular computers
\end{itemize}
The ``secret sauce'' is the golden ratio ($\phi \approx 1.618$), a special number that appears throughout nature. By using this number in our calculations, we can find hidden patterns in data.}

The system implements:
\begin{enumerate}
  \item \textbf{7 unitary transform variants} (unitary by construction) with distinct spectral properties
  \item \textbf{Hybrid compression pipelines} achieving 37\% improvement on mixed signals
  \item \textbf{Experimental 48-round Feistel cipher} with ~50\% avalanche (no formal proofs)
  \item \textbf{Synthesizable SystemVerilog RTL} for FPGA deployment
  \item \textbf{React Native mobile app} and PyQt5 desktop applications
\end{enumerate}}

@@

@@

\begin{itemize}
  \item \texttt{spdx-headers.yml} --- Automatically adds license headers to all files
\end{itemize}

@@

The SPDX workflow distinguishes between AGPL-3.0 files and Claims-NC files using the list in \texttt{CLAIMS\_PRACTICING\_FILES.txt}. The agent spec defines TODO items for:
\begin{enumerate}
  \item WaveField abstraction layer
  \item Binary-to-WaveField middleware
  \item Audio/Visual/Physics/Crypto labs
  \item Comprehensive test coverage
\end{enumerate}}

@@

@@

  \item \textbf{Step 1 (FFT):} Break the signal into its frequency components---like separating a chord into individual notes
  \item \textbf{Step 2 (Chirp):} Add a ``swirl'' to each frequency based on its position squared
  \item \textbf{Step 3 (Golden Twist):} Add another twist based on the golden ratio---this is what makes RFT special
\end{enumerate}

The magic is that this process is \textbf{perfectly reversible}. Apply the inverse transform and you get your original data back exactly (within computer precision limits of about 0.00000000000001\% error).
}

@@

@@

@@

@@

    except ImportError:
        return {
            'native_available': False,
            'implementation': 'python',
            'version': 'numpy-fft'
        }

@@

  \item \textbf{Original:} The classic golden-ratio version
  \item \textbf{Chaotic:} For random-looking data
  \item \textbf{Fibonacci:} For data with integer patterns
  \item \textbf{Harmonic:} For curved/smooth data
  \item \textbf{Adaptive:} Automatically picks the best flavor
\end{itemize}
All flavors are ``unitary''---they all preserve energy perfectly.}

@@

@@

@@

  \item \textbf{Lossless:} Perfect reconstruction (like ZIP files)
  \item \textbf{Hybrid:} Combines multiple techniques for best results on mixed data
\end{itemize}}

@@

        for name, tensor in state_dict.items():
            encoded[name] = self.encode_tensor(tensor.numpy())
        return encoded

@@

@@

@@

@@

%==============================================================================

@@

@@

@@

@@

@@

%==============================================================================

@@

@@

%==============================================================================

@@

\begin{tabular}{@{}ll@{}}
\toprule
\textbf{File/Directory} & \textbf{Purpose} \\
\midrule
\texttt{App.tsx} & Main entry point with splash screen \\
\texttt{app.json} & Expo configuration \\
\texttt{package.json} & Node.js dependencies \\
\texttt{src/algorithms/} & Mobile RFT implementations \\
\texttt{src/components/} & Reusable UI components \\
\texttt{src/screens/} & App screens (home, settings, etc.) \\
\texttt{src/navigation/} & React Navigation setup \\
\texttt{src/utils/} & Utility functions \\
\texttt{src/constants/} & App constants and themes \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{tabular}{@{}p{5.5cm}p{7.5cm}@{}}
\toprule
\textbf{Script} & \textbf{Purpose} \\
\midrule
\multicolumn{2}{l}{\textit{Validation Scripts}} \\
\texttt{irrevocable\_truths.py} & Validates 7 variants and fundamental theorems \\
\texttt{verify\_scaling\_laws.py} & Verifies compression scaling laws \\
\texttt{verify\_rate\_distortion.py} & Rate-distortion analysis \\
\texttt{verify\_braided\_comprehensive.py} & Braided structure validation \\
\texttt{validate\_paper\_claims.py} & Validates claims from research paper \\
\midrule
\multicolumn{2}{l}{\textit{Generation Scripts}} \\
\texttt{generate\_all\_theorem\_figures.py} & Generate figures for all theorems \\
\texttt{generate\_rft\_gifs.py} & Create animated RFT visualizations \\
\texttt{generate\_pdf\_figures\_for\_latex.py} & PDF figures for LaTeX papers \\
\texttt{generate\_rft\_gifs\_simple.py} & Simplified GIF generation \\
\midrule
\multicolumn{2}{l}{\textit{Utility Scripts}} \\
\texttt{quantonium\_boot.py} & Desktop boot/launcher \\
\texttt{build.py} & Build system script \\
\texttt{md\_to\_pdf.py} & Markdown to PDF converter \\
\texttt{analyze\_quantum\_chaos.py} & Quantum chaos metrics \\
\texttt{compile\_paper.sh} & Compile LaTeX papers \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{tabular}{@{}p{5cm}p{8cm}@{}}
\toprule
\textbf{Tool} & \textbf{Purpose} \\
\midrule
\multicolumn{2}{l}{\textit{Benchmarking}} \\
\texttt{uspto\_benchmark\_suite.py} & Generate USPTO patent evidence \\
\texttt{benchmark\_runner.py} & Run performance benchmarks \\
\midrule
\multicolumn{2}{l}{\textit{Compression}} \\
\texttt{compression\_pipeline.py} & Full compression pipeline \\
\texttt{rft\_hybrid\_compress.py} & Hybrid RFT compression \\
\texttt{rft\_encode\_model.py} & Encode model weights \\
\texttt{rft\_decode\_model.py} & Decode model weights \\
\texttt{real\_hf\_model\_compressor.py} & HuggingFace model compression \\
\midrule
\multicolumn{2}{l}{\textit{Development}} \\
\texttt{spdx\_inject.py} & Add SPDX license headers \\
\texttt{generate\_repo\_inventory.py} & Generate repository inventory \\
\texttt{restructure\_dry\_run.py} & Preview restructuring changes \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Directory} & \textbf{Investigation} \\
\midrule
\texttt{ascii\_wall/} & Testing compression on pure ASCII text \\
\texttt{corpus/} & Benchmark corpus (text, audio, image samples) \\
\texttt{entropy/} & Entropy analysis of RFT coefficients \\
\texttt{fibonacci/} & Fibonacci sequence compression \\
\texttt{hypothesis\_testing/} & Statistical validation of claims \\
\texttt{sota\_benchmarks/} & State-of-the-art comparisons \\
\texttt{tetrahedral/} & Tetrahedral lattice experiments \\
\bottomrule
\end{tabular}
\end{center}

@@

\begin{verbatim}
# Create isolated Python environment
python3 -m venv .venv

@@

\begin{verbatim}
# Build the image
docker build -t quantoniumos .

@@

%------------------------------------------------------------------------------

@@

@@

@@

@@

@@
